---
title: "Week 4"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(nycflights13)
library(ggplot2)
library(dplyr)
```

Q1: What time of day should you fly if you want to avoid delays as much as possible?
```{r}
flights %>%
  group_by(hour) %>%
  summarise(arr_delay = mean(arr_delay, na.rm = T),dep_delay=mean(dep_delay, na.rm = T)) 
```
5am-10am.

Q2: Does this choice depend on anything? Season? Weather? Airport? Airline?

One: Season
```{r}
Season_flights <- flights %>%
  mutate(season = ifelse(month >= 3 & month <= 5, 'spring', 
                         ifelse(month>=6 & month <= 8, "summer",
                                ifelse(month>=9&month <=11, "autumn","winter"))))%>%
  group_by(season)%>%
  summarise(dep_delay=mean(dep_delay, na.rm = T))%>%
  arrange(dep_delay)

ggplot(Season_flights, aes(x=season, y=dep_delay))+
  geom_bar(stat="identity")+
  labs(x="Season",
       y="Departure Delay")
```

The four seasons of depature delay time from longest to shortest are summer, spring, winter, and autumn.

Two: Airport
```{r}
Airport_flights <- flights %>%
  group_by(origin) %>%
  mutate(dep_delay_lag = lag(dep_delay)) %>%
  arrange(dep_delay) 

ggplot(Airport_flights, aes(y = dep_delay, x = origin)) +
  geom_bar(stat = "identity") +
  labs(x = "Departure Delay",
       y = "Delay time")
```
The EWR has the most depature delay time, and the LGA has the least depature delay time.

Three: Airlines
```{r}
Airlines_flights <- flights %>%
  group_by(carrier) %>%
  summarise(dep_delay = mean(dep_delay,na.rm = T))%>%
  arrange(dep_delay)

ggplot(Airlines_flights, aes(x=carrier, y=dep_delay))+
  geom_bar(stat = "identity") +
  labs(x="Carrier",
       y="Departure Delay Time")
```

I would choose AS, HA, and US airlines because their departure delay time is shorter.

